\scshape Topics in mechanism design

### 2023-11-06 ch1.tex
Add files via upload

We may thus focus on IC mechanisms that induce participation (or are `individually rational', aka `IR'),
meaning that every type $t$'s payoff $t q(t) - p(t)$ is non-negative.

@@

\begin{exercise}
	%
	\label{exercise:posted_price}
	%
	(a) This allocation--payment pair (viewed as a direct mechanism) is IC; why?
	(b) Verify that this mechanism satisfies the envelope formula.
	(c) There are other mechanisms $(q,p')$, i.e. they have the same allocation but different payments. Describe them.
	%
\end{exercise}

@@

Note that $\mathcal{Q}$ is a convex space: if $q$ and $q'$ are both increasing maps $[0,1] \to [0,1]$, then so is $\alpha q + (1-\alpha) q'$ for any scalar $\alpha \in [0,1]$.
Note further that the objective $R$ is linear:
%
\begin{equation*}
	R( \alpha q + (1-\alpha) q' ) = \alpha R(q) + (1-\alpha) R(q') 
	\quad \text{for any $q,q' \in \mathcal{Q}$ and $\alpha \in [0,1]$.}
\end{equation*}
%
$R$ is also continuous in a suitable sense.
Finally, $\mathcal{Q}$ is (in fact) compact in a suitable sense.%
	\footnote{It is compact in the product topology (=the topology of pointwise convergence).
	Proof: it is a closed subset of the space of all functions $[0,1] \to [0,1]$, which is compact by Tychonoff's theorem.}

@@

This intuition is incomplete, it seems to me, at least when $\inf S > 0$, because `perfect competition' surely means selling at marginal cost (which we've normalised to zero), rather than at price $\inf S$!
Here's a better intuition: (1) the seller always has enough bargaining power to extract the surplus $\inf S - 0 = \inf S$, because she (not the buyer) is the one who makes the offers, but (2) as $\Delta \to 0$, any \emph{additional} bargaining power that she has vanishes because she must compete against her next-period self.

@@

Each type $t \in \mathcal{T}$ of the agent has a belief $\mu(t)$ about how likely various signal realisations are.
Formally, \emph{belief} (about the signal) is a vector $\mu \in [0,1]^{\abs*{\mathcal{X}}}$ whose entries sum to unity. We write $\Delta$ for the set of all beliefs.

@@

In the proof, `side bet' $b(t)$ is a monetary gamble on the signal; it has zero expected value for type $t$, but strictly positive expected value for all the other types.
By tacking a sufficiently blown-up version of this gamble onto the payment rule $p$,
we ensure that the agent's incentive to choose the right \emph{gamble} overwhelms all other considerations:
she reports truthfully regardless.

>>>>

We may thus focus on IC mechanisms $(q,p)$ that induce participation, i.e. those such that every type $t$'s payoff $t q(t) - p(t)$ is non-negative. Such mechanisms are called \emph{individually rational (IR).}

@@

\begin{exercise}
	%
	\label{exercise:posted_price}
	%
	(a) This allocation--payment pair (viewed as a direct mechanism) is IC; why?
	(b) Verify that this mechanism satisfies the envelope formula.
	(c) There are other mechanisms $(q,p')$, i.e. mechanisms with the same allocation but different payments. Describe them.
	%
\end{exercise}

@@

Note that $\mathcal{Q}$ is a convex space: if $q$ and $q'$ are both increasing maps $[0,1] \to [0,1]$, then so is $\alpha q + (1-\alpha) q'$ for any scalar $\alpha \in [0,1]$.
Note further that the objective $R$ is linear:
%
\begin{equation*}
	R( \alpha q + (1-\alpha) q' ) = \alpha R(q) + (1-\alpha) R(q') 
	\quad \text{for any $q,q' \in \mathcal{Q}$ and $\alpha \in [0,1]$.}
\end{equation*}
%
$R$ is also continuous in a suitable sense.
Finally, $\mathcal{Q}$ is (in fact) compact in a suitable sense.

@@

This intuition is incomplete, it seems to me, at least when $\inf S > 0$, because `perfect competition' surely means selling at marginal cost (which we've normalised to zero), rather than at price $\inf S$!
Here's a better intuition from Francesco Nava (who has several papers on this topic): the seller's lack of commitment constrains her eventually to sell the good whatever the buyer's value, and constrains her no further than that; thus she sells the good at the highest market-clearing price, which is $\inf S$.

@@

Each type $t \in \mathcal{T}$ of the agent has a belief $\mu(t)$ about how likely various signal realisations are.
Formally, a \emph{belief} (about the signal) is a vector $\mu \in [0,1]^{\abs*{\mathcal{X}}}$ whose entries sum to unity. We write $\Delta$ for the set of all beliefs.

@@

In the proof, the `side bet' $b(t)$ is a monetary gamble on the signal; it has zero expected value for type $t$, but strictly positive expected value for all the other types.
By tacking a sufficiently blown-up version of this gamble onto the payment rule $p$,
we ensure that the agent's incentive to choose the right \emph{gamble} overwhelms all other considerations:
she reports truthfully regardless.

### 2023-11-06 ch2.tex
Add files via upload

`Who gets what?' is perhaps the most fundamental question in economics.
This chapter concerns recent research on that question.

@@

In many models, each agent $i$ privately knows her type $t_i$.
We can imagine three stages:
the (perhaps fictional) \emph{ex-ante} stage at which agents do not know anyone's type,
the \emph{interim} stage at which agents know their own types but not those of others,
and the \emph{ex-post} stage at which all agents' types are common knowledge.

@@

Suppose you give me a \emph{candidate interim allocation,}
meaning a collection $(Q_i)_{i=1}^I$ of (measurable) functions, where $Q_i$ maps $\mathcal{T}_i$ into $[0,1]$.
Can I always construct an allocation $q$ that realises this collection as its interim allocation?
(No. Find a counter-example!)

@@

We won't prove this; instead we'll introduce and prove a symmetric version.
Call the environment \emph{symmetric} iff all agents' types are drawn from the same type space, call it $\mathcal{T}$,
according to the same distribution, call it $\mu$.
A \emph{symmetric candidate interim allocation} is a (measurable) map $Q : \mathcal{T} \to [0,1]$;
we interpret this as the candidate interim allocation $(Q_i)_{i=1}^I$ in which $Q_i = Q$ for every $i$.
A symmetric allocation $q$ is one such that $q(\boldsymbol{t}) = q(\boldsymbol{t'})$ whenever $\boldsymbol{t'}$ is a permutation of $\boldsymbol{t}$.

@@

\begin{proof}[Proof that \ref{bullet:border_sym:ineq} implies \ref{bullet:border_sym:real}, finite case]
	%
	Assume that $\mathcal{T}$ is finite, and (wlog) that $\mu$ is strictly positive.
	We shall prove the contra-positive:
	fix a candidate interim allocation $Q$ that is not realisable;
	we shall find a set $T \subseteq \mathcal{T}$
	for which the relevant Border inequality fails.

@@

\begin{remark}
	%
	\label{remark:border_altproof}
	%
	Gregorio Curello proposes an alternative strategy for proving that \ref{bullet:border_sym:ineq} implies \ref{bullet:border_sym:real},
	taking inspiration from \textcite{KleinerMoldovanuStrack2021}.
	Write $\mathcal{B}$ for the set of symmetric candidate interim allocations that satisfy the Border inequalities; we must show that every $Q \in \mathcal{B}$ is realised by some symmetric allocation.
	It suffices to show that every extreme point of $\mathcal{B}$ is realisable.%
		\footnote{Suppose we know that every $Q' \in \ext \mathcal{B}$ is realised by some symmetric allocation, call it $q^{Q'}$.
		Fix some $Q \in \mathcal{B}$.
		By Choquet's theorem (see the next section), there is a probability measure $\mu$ defined on the extreme points $\ext \mathcal{B}$
		such that
		$\smash{Q = \int_{\ext \mathcal{B}} Q' \mu( \dd Q' )}$.
		Then $Q$ is realised by the symmetric allocation
		$\smash{q = \int_{\ext \mathcal{B}} q^{Q'} \mu( \dd Q' )}\vphantom{\int_{\ext \mathcal{B}}}$.}
	It is possible to characterise the extreme points of $\mathcal{B}$ in a reasonably nice fashion.%
		\footnote{\textcite{KleinerMoldovanuStrack2021} characterise the extreme points of a subset (viz. the set of those $Q \in \mathcal{B}$ that are also increasing),
		and indicate that a characterisation of the extreme points of $\mathcal{B}$ itself exists (they cite \textcite{Ryff1967}).
		\emph{Note:} these authors use different language; in particular, they show that membership of $\mathcal{B}$ may be interpreted as satisfaction of a majorisation constraint, and their result characterises the extreme points of any space of monotone functions satisfying a majorisation constraint.}
	And Gregorio and I conjecture that one can use this characterisation to show that any extreme point of $\mathcal{B}$
	is realisable;
	specifically, by some hierarchical allocation.
	(Small correction: 
	whereas we defined hierarchical allocations to have finitely many sets $R_1,\dots,R_K$, I think that this claim is true only if infinitely many sets are permitted.)
	%
\end{remark}

@@

	So take any $Q \in \mathcal{Q}$;
	by Choquet's theorem, $Q = \int_{\ext \mathcal{Q}} Q' \mu( \dd Q' )$.
	Each $Q' \in \ext \mathcal{Q}$ is realised by a $q^{Q'}$
	that is either $0$ or a symmetric hierarchical allocation with $q^{Q'}_1(\cdot,\boldsymbol{t_{-1}})$ increasing.
	Thus $Q$ is realised by the allocation
	%
	\begin{equation*}
		q \coloneqq \int_{\ext \mathcal{Q}} q^{Q'} \dd \mu( \dd Q' ) ,
	\end{equation*}
	%
	which is evidently symmetric and has $q_1(\cdot,\boldsymbol{t_{-1}})$ increasing.
	%
\end{proof}

\paragraph{The literature.}
The theorem is due to \textcite{ManelliVincent2010};
their proof is more involved.%
	\footnote{Rather than using Choquet's theorem, they rely on the weaker Krein--Milman theorem; this necessitates an additional limit argument.}
See \textcite{GershkovEtAl2013} for a generalisation using a different technique, and \textcite{KleinerMoldovanuStrack2021} for yet another generalisation, using yet another technique.
Equivalence generally fails if agents' types are multi-dimensional \parencite{JehielMoldovanuStacchetti1999}, as is the case when there are multiple goods (recall §\ref{sec:ch1:multi-d}).

@@

Applying the reasoning of \cref{ch1} agent-by-agent (in a similar way to how we reasoned agent-by-agent in the proof of \Cref{lemma:impl_mon} above)
yields that any Bayesian IC mechanism $(q,p)$ must satisfy the envelope formula
%
\begin{equation*}
	P_i(t_i) = -P_i(0) + t_i Q_i(t_i) - \int_0^{t_i} Q_i
	\quad \text{for every $t_i \in [0,1]$ and $i$,}
\end{equation*}
%
that (interim) IR requires exactly that $P_i(0) \leq 0$ for each $i$,
and thus that revenue-maximising mechanisms have $P_i(0)=0$ for every $i$.
This reduces the revenue-maximisation problem to choosing an allocation $q$ to maximise
%
\begin{equation*}
	R(q) \coloneqq \sum_{i=1}^I R_i(Q_i) ,
	\quad \text{where} \quad
	R_i(Q_i)
	\coloneqq \E\left( T_i Q_i(T_i) - \int_0^{T_i} Q_i \right) ,
\end{equation*}
%
subject to the constraint that $Q_i$ be increasing for each agent $i$.

@@

\begin{namedthm}[The Bulow--Klemperer theorem.]
	%
	\label{theorem:BulowKlemperer}
	%
	In the symmetric regular smooth IPV model,
	for any $I \in \N$,
	the expected revenue of the revenue-maximising mechanism with $I$ bidders
	is weakly lower than the expected revenue of the second-price auction with $I+1$ bidders.
	%
\end{namedthm}

>>>>

`Who gets what?' is perhaps the most fundamental question in economics.
This chapter concerns research on that question.

@@

In many models, each agent $i$ privately knows her type $t_i$.
We can imagine three stages:
an \emph{ex-ante} stage at which agents do not know anyone's type,
an \emph{interim} stage at which agents know their own types but not those of others,
and an \emph{ex-post} stage at which all agents' types are common knowledge.

@@

Suppose you give me a \emph{candidate interim allocation,}
meaning a collection $(Q_i)_{i=1}^I$ of (measurable) functions, where $Q_i$ maps $\mathcal{T}_i$ into $[0,1]$.
Can I always construct an allocation $q$ that realises this collection as its interim allocation?
(No: consider $\mathcal{T}_i = [0,1]$, $\mu_i$ with full support, and $Q_i(t_i) = 0$ if $t_i<1/2$ and $Q_i(t_i)=1$ otherwise, for all agents $i$.)

@@

We won't prove this; instead we'll introduce and prove a symmetric version.
Call the environment \emph{symmetric} iff all agents' types are drawn from the same type space, call it $\mathcal{T}$,
according to the same distribution, call it $\mu$.
A \emph{symmetric candidate interim allocation} is a (measurable) map $Q : \mathcal{T} \to [0,1]$;
we interpret this as the candidate interim allocation $(Q_i)_{i=1}^I$ in which $Q_i = Q$ for every $i$.
An allocation $q$ is \emph{symmetric} iff agents' treatment does not depend on their names/labels:
for any type profiles $\boldsymbol{t}$ and $\boldsymbol{t'}$ that differ only in that $i$'s and $j$'s types are reversed, $q(\boldsymbol{t})$ and $q(\boldsymbol{t'})$ differ only in that $i$'s and $j$'s probabilities are reversed.%
	\footnote{That is: for any $\boldsymbol{t} = (t_1,\dots,t_I)$ and $\boldsymbol{t'} = (t_1',\dots,t_I')$ such that $t_i = t_j'$, $t_j = t_i'$ and $t_k = t_k'$ for every $k \in \{1,\dots,I\} \setminus \{i,j\}$, we have $q_i(\boldsymbol{t}) = q_j(\boldsymbol{t'})$, $q_j(\boldsymbol{t}) = q_i(\boldsymbol{t'})$, and $q_k(\boldsymbol{t}) = q_k(\boldsymbol{t'})$ for every $k \in \{1,\dots,I\} \setminus \{i,j\}$.}

@@

\begin{proof}[Proof that \ref{bullet:border_sym:ineq} implies \ref{bullet:border_sym:real}, finite case]
	%
	Assume that $\mathcal{T}$ is finite, and (wlog) that $\mu$ is strictly positive.
	We shall prove the contra-positive:
	fix a candidate interim allocation $Q$ that is not realisable;
	we shall find a set $T \subseteq \mathcal{T}$ on which the relevant Border inequality fails.

@@

% \begin{remark}
% 	%
% 	\label{remark:border_altproof}
% 	%
% 	Gregorio Curello proposes an alternative strategy for proving that \ref{bullet:border_sym:ineq} implies \ref{bullet:border_sym:real},
% 	taking inspiration from \textcite{KleinerMoldovanuStrack2021}.
% 	Write $\mathcal{B}$ for the set of symmetric candidate interim allocations that satisfy the Border inequalities; we must show that every $Q \in \mathcal{B}$ is realised by some symmetric allocation.
% 	It suffices to show that every extreme point of $\mathcal{B}$ is realisable.%
% 		\footnote{Suppose we know that every $Q' \in \ext \mathcal{B}$ is realised by some symmetric allocation, call it $q^{Q'}$.
% 		Fix some $Q \in \mathcal{B}$.
% 		By Choquet's theorem (see the next section), there is a probability measure $\mu$ defined on the extreme points $\ext \mathcal{B}$
% 		such that
% 		$\smash{Q = \int_{\ext \mathcal{B}} Q' \mu( \dd Q' )}$.
% 		Then $Q$ is realised by the symmetric allocation
% 		$\smash{q = \int_{\ext \mathcal{B}} q^{Q'} \mu( \dd Q' )}\vphantom{\int_{\ext \mathcal{B}}}$.}
% 	It is possible to characterise the extreme points of $\mathcal{B}$ in a reasonably nice fashion.%
% 		\footnote{\textcite{KleinerMoldovanuStrack2021} characterise the extreme points of a subset (viz. the set of those $Q \in \mathcal{B}$ that are also increasing),
% 		and indicate that a characterisation of the extreme points of $\mathcal{B}$ itself exists (they cite \textcite{Ryff1967}).
% 		\emph{Note:} these authors use different language; in particular, they show that membership of $\mathcal{B}$ may be interpreted as satisfaction of a majorisation constraint, and their result characterises the extreme points of any space of monotone functions satisfying a majorisation constraint.}
% 	And Gregorio and I conjecture that one can use this characterisation to show that any extreme point of $\mathcal{B}$
% 	is realisable;
% 	specifically, by some hierarchical allocation.
% 	(Small correction: 
% 	whereas we defined hierarchical allocations to have finitely many sets $R_1,\dots,R_K$, I think that this claim is true only if infinitely many sets are permitted.)
% 	%
% \end{remark}

@@

	So take any $Q \in \mathcal{Q}$;
	by Choquet's theorem, $Q = \int_{\ext \mathcal{Q}} Q' \mu( \dd Q' )$.
	Each $Q' \in \ext \mathcal{Q}$ is realised by a $q^{Q'}$
	that is either $0$ or a symmetric hierarchical allocation with $q^{Q'}_1(\cdot,\boldsymbol{t_{-1}})$ increasing.
	Thus $Q$ is realised by the allocation
	%
	\begin{equation*}
		q \coloneqq \int_{\ext \mathcal{Q}} q^{Q'} \mu( \dd Q' ) ,
	\end{equation*}
	%
	which is evidently symmetric and has $q_1(\cdot,\boldsymbol{t_{-1}})$ increasing.
	%
\end{proof}

\paragraph{The literature.}
The theorem is due to \textcite{ManelliVincent2010};
their proof is more involved.%
	\footnote{Rather than using Choquet's theorem, they rely on the weaker Krein--Milman theorem; this necessitates an additional limit argument.}
See \textcite{GershkovEtAl2013} for a generalisation using a different technique, and \textcite{KleinerMoldovanuStrack2021} for yet another generalisation, using yet another technique.
Equivalence generally fails if agents' types are multi-dimensional \parencite{JehielMoldovanuStacchetti1999}, as is the case when there are multiple goods (recall §\ref{sec:ch1:multi-d}).
\textcite{JeongPycia2023} use reasoning similar to that of this section to show that every extreme point of the space of all symmetric IC mechanisms is induced by a (slightly generalised) first-price auction.

@@

Applying the reasoning of \cref{ch1} agent-by-agent (in a similar way to how we reasoned agent-by-agent in the proof of \Cref{lemma:impl_mon} above)
yields that any Bayesian IC mechanism $(q,p)$ must satisfy the envelope formula
%
\begin{equation*}
	P_i(t_i) = P_i(0) + t_i Q_i(t_i) - \int_0^{t_i} Q_i
	\quad \text{for every $t_i \in [0,1]$ and $i$,}
\end{equation*}
%
that (interim) IR requires exactly that $P_i(0) \leq 0$ for each $i$,
and thus that revenue-maximising mechanisms have $P_i(0)=0$ for every $i$.
This reduces the revenue-maximisation problem to choosing an allocation $q$ to maximise
%
\begin{equation*}
	R(q) \coloneqq \sum_{i=1}^I R_i(Q_i) ,
	\quad \text{where} \quad
	R_i(Q_i)
	\coloneqq \E\left( T_i Q_i(T_i) - \int_0^{T_i} Q_i \right) ,
\end{equation*}
%
subject to the constraint that $Q_i$ be increasing for each agent $i$.

@@

\begin{namedthm}[Bulow--Klemperer theorem.]
	%
	\label{theorem:BulowKlemperer}
	%
	In the symmetric regular smooth IPV model,
	for any $I \in \N$,
	the expected revenue of the revenue-maximising mechanism with $I$ bidders
	is weakly lower than the expected revenue of the second-price auction with $I+1$ bidders.
	%
\end{namedthm}

### 2023-11-06 ch3.tex
Add files via upload

Since there are a lot of periods, let's simplify by having only two types $t \in \{\ell,h\}$.
We assume that $0 < \ell < c < h$,
so that the principal wishes to allocate only to high types,
while all types of the agent want the good (though high types want it more).

@@

The analysis differs slightly depending on when the agent learns her type.
In §\ref{sec:ch3:token}, we shall assume that the agent learns the realisation of her entire type sequence $(T_n)_{n=0}^\infty$ at the outset (period $n=0$).
In §\ref{sec:ch3:guohorner}--§\ref{sec:ch3:nocommitment}, we shall instead assume that the agent learns the realisation of $T_n$ only at the dawn of period $n$, for each $n \in \{0,1,\dots,\}$.

@@

Assume (mostly for simplicity) that the agent learns the realisation of her entire type sequence $(T_n)_{n=0}^\infty$ at the outset.

@@

We could just as well replace this lifetime budget constraint with a dynamic budget constraint: the agent starts out with $M_0$ `tokens',
which may be spent to obtain the good and which accrue interest at rate $\delta^{-1}-1$ if saved:
%
\begin{equation*}
	q_n + M_{n+1}
	\leq \delta^{-1} M_n 
	\quad \text{in each period $n$.}
\end{equation*}
%
We impose the no-Ponzi-scheme condition
%
\begin{equation*}
	\lim_{n \to \infty} \delta^n M_n = 0 .
\end{equation*}
%
Then we have
%
\begin{align*}
	M_0
	&\geq \delta M_1 + \delta q_0
	\\
	&\geq \delta ( \delta M_2 + \delta q_1 )
	+ \delta q_0
	= \delta^2 M_2
	+ \delta ( q_0 + \delta q_1 )
	\\
	&\geq \delta^2 ( \delta M_3 + \delta q_2 )
	+ \delta ( q_0 + \delta q_1 )
	= \delta^3 M_3
	+ \delta \left( q_0 + \delta q_1 + \delta^2 q_2 \right)
	\\
	&\;\; \vdots
	\\
	&\geq \lim_{n \to \infty} \delta^n M_n
	+ \delta \sum_{n=0}^\infty \delta^n q_n 
	= \delta \sum_{n=0}^\infty \delta^n q_n ,
\end{align*}
%
or
%
\begin{equation*}
	(1-\delta) \sum_{n=0}^\infty \delta^n q_n
	\leq (1-\delta) \delta^{-1} M_0
	\eqqcolon K.
\end{equation*}

@@

\begin{proof}
	%
	Fix a cap $K \in [0,1]$ and a discount factor $\delta \in (0,1)$.
	Clearly the agent always exhausts the budget.
	If $Q_\delta \geq K$, then she consumes only when $T_n=h$,
	so her payoff is $h K$.
	If $Q_\delta < K$, then the agent consumes whenever $T_n=h$,
	and spends the rest of the budget when $T_n=\ell$;
	thus her payoff is $h Q_\delta + \ell (K-Q_\delta)$.
	The principal's payoff is the agent's payoff minus $cK$, so
	%
	\begin{multline*}
		(h-c) Q_\delta
		- U_\delta^K
		\\
		\begin{aligned}
			&= (h-c) Q_\delta
			- \Bigl[
			h \min\{K,Q_\delta\}
			+ \ell \min\{K-Q_\delta,0\}
			- c K 
			\Bigr]
			\\
			&= (h-c) Q_\delta
			+ \Bigl[
			h \max\{-K,-Q_\delta\}
			+ \ell \max\{Q_\delta-K,0\}
			+ c K 
			\Bigr]
			\\
			&= (h+\ell) \max\{Q_\delta-K,0\}
			- c (Q_\delta-K) .			
		\end{aligned}		
	\end{multline*}
	%
	For $K=p$,
	as $\delta \uparrow 1$,
	the right-hand side vanishes a.s.
	since $Q_\delta \to p$ a.s.
	by a strong law of large numbers for discounted sums \parencite[see][]{Lai1974}.
	%
\end{proof}

@@

\paragraph{The literature.}
\textcite{JacksonSonnenschein2007} showed that the principal's first-best can be approximated by `linking' the allocations across different periods via something like a discounted quota.
(The theorem in this paper is true as stated, but the proof is wrong: see \textcite{BallJacksonKattwinkel2022} for the correction.)
\textcite{MatsushimaMiyazakiYagi2010,Ishii2016} go further, characterising the full set of allocations that are (virtually) implementable via quota mechanisms.
(The characterisation: virtual implementability via quotas is equivalent to implementability using monetary transfers.)
\textcite{Frankel2016jet} is a clear-eyed and general formulation of the quotas idea, with good references references to related work.
\textcite{Frankel2016aej} provides a similarly insightful and general treatment of the idea in \Cref{remark:het}.
(None of these papers considers precisely the model above,
and the mechanism in Jackson--Sonnenschein is not quite a discounted-quota mechanisms.)

>>>>

Let's simplify by having only two types $t \in \{\ell,h\}$.
We assume that $0 < \ell < c < h$,
so that the principal wishes to allocate only to high types,
while all types of the agent want the good (though high types want it more).

@@

The analysis differs depending on when the agent learns her type.
In §\ref{sec:ch3:token}, we shall assume that the agent learns the realisation of her entire type sequence $(T_n)_{n=0}^\infty$ at the outset (period $n=0$).
In §\ref{sec:ch3:guohorner}--§\ref{sec:ch3:nocommitment}, we shall instead assume that the agent learns the realisation of $T_n$ only at the dawn of period $n$, for each $n \in \{0,1,\dots,\}$.

@@

Assume that the agent learns the realisation of her entire type sequence $(T_n)_{n=0}^\infty$ at the outset.%
	\footnote{My own intuition suggests that this assumption shouldn't matter much, but I may be wrong. There is no definitive answer in the literature, to my knowledge.}

@@

We could just as well replace this lifetime budget constraint with a dynamic budget constraint: the agent starts out with $M_0 \coloneqq (1-\delta) \delta^{-1} K$ `tokens',
which may be spent to obtain the good and which accrue interest at rate $\delta^{-1}-1$ if saved:
%
\begin{equation*}
	q_n + M_{n+1}
	\leq \delta^{-1} M_n 
	\quad \text{in each period $n$.}
\end{equation*}
%
We impose the no-Ponzi-scheme condition
%
\begin{equation*}
	\lim_{n \to \infty} \delta^n M_n = 0 .
\end{equation*}
%
Then we have
%
\begin{align*}
	M_0
	&\geq \delta M_1 + \delta q_0
	\\
	&\geq \delta ( \delta M_2 + \delta q_1 )
	+ \delta q_0
	= \delta^2 M_2
	+ \delta ( q_0 + \delta q_1 )
	\\
	&\geq \delta^2 ( \delta M_3 + \delta q_2 )
	+ \delta ( q_0 + \delta q_1 )
	= \delta^3 M_3
	+ \delta \left( q_0 + \delta q_1 + \delta^2 q_2 \right)
	\\
	&\;\; \vdots
	\\
	&\geq \lim_{n \to \infty} \delta^n M_n
	+ \delta \sum_{n=0}^\infty \delta^n q_n 
	= \delta \sum_{n=0}^\infty \delta^n q_n ,
\end{align*}
%
or
%
\begin{equation*}
	(1-\delta) \sum_{n=0}^\infty \delta^n q_n
	\leq K.
\end{equation*}

@@

\begin{proof}
	%
	Fix a cap $K \in [0,1]$ and a discount factor $\delta \in (0,1)$.
	Clearly the agent always exhausts the budget.
	If $Q_\delta \geq K$, then she consumes only when $T_n=h$,
	so her payoff is $h K$.
	If $Q_\delta < K$, then the agent consumes whenever $T_n=h$,
	and spends the rest of the budget when $T_n=\ell$;
	thus her payoff is $h Q_\delta + \ell (K-Q_\delta)$.
	The principal's payoff is the agent's payoff minus $cK$, so
	%
	\begin{multline*}
		(h-c) Q_\delta
		- U_\delta^K
		\\
		\begin{aligned}
			&= (h-c) Q_\delta
			- \Bigl[
			h \min\{K,Q_\delta\}
			+ \ell \max\{K-Q_\delta,0\}
			- c K 
			\Bigr]
			\\
			&= (h-c) Q_\delta
			- \Bigl[
			- h \max\{-K,-Q_\delta\}
			+ \ell \max\{K-Q_\delta,0\}
			- c K 
			\Bigr]
			\\
			&= (h-c) Q_\delta
			- \Bigl[
			- (h-\ell) \max\{K-Q_\delta,0\}
			+ (h-c)K
			\Bigr]
			\\
			&= - (h-c) ( K - Q_\delta )
			+ (h-\ell) \max\{K-Q_\delta,0\} .			
		\end{aligned}
	\end{multline*}
	%
	For $K=p$,
	as $\delta \uparrow 1$,
	the right-hand side vanishes a.s.
	since $Q_\delta \to p$ a.s.
	by a strong law of large numbers for discounted sums \parencite[see][]{Lai1974}.
	%
\end{proof}

@@

\paragraph{The literature.}
\textcite{JacksonSonnenschein2007} showed that the principal's first-best can be approximated by `linking' the allocations across different periods via something like a discounted quota.
(The theorem in this paper is true as stated, but the proof is wrong: see \textcite{BallJacksonKattwinkel2022} for the correction.)
\textcite{BallKattwinkel2023} go further, characterising the full set of allocations that are implementable via quota mechanisms,%
	\footnote{The result: all and only those that could be implemented using monetary transfers! This result refines an earlier characterisation due to \textcite{MatsushimaMiyazakiYagi2010,Ishii2016}, which concerns \emph{virtual} implementability. (There is a mistake in the former paper; see \textcite{BallKattwinkel2023comment} for the correction.)}
and proving a number of robustness results. (I highly recommend this paper.)
\textcite{Frankel2016jet} is a clear-eyed and general formulation of the quotas idea, with good references references to related work.
\textcite{Frankel2016aej} provides a similarly insightful and general treatment of the idea in \Cref{remark:het}.
(None of these papers considers precisely the model above,
and the mechanisms in Jackson--Sonnenschein and Ball--Kattwinkel are not quite discounted-quota mechanisms in the sense of this chapter.)

### 2023-11-06 ms.tex
Add files via upload

% % watermark on every page (for version control)
% \usepackage[anchor=ll,pos={0.1cm,0.5cm},fontsize=0.2cm,angle=0,alignment=l]{draftwatermark}
% \SetWatermarkText{\normalfont \, version:\\\normalfont {\datestyle\today}\\\normalfont \, at {\currenttime}}

@@

\date{\small This version: 5 September 2023}

@@

These are the notes for a second-year graduate course that I taught at Oxford in the autumns of 2021 and 2022.
Thanks to Gregorio Curello, Deniz Kattwinkel, Elliot Lipnowski, Qingmin Liu, Alex Teytelboym and to my students for comments, suggestions and insights,
and to Catharina Behrens, Josh le Cornu, Tanxin Gao, Brooklyn Han, Simon Handreke, Sanjari Kalantri, Marie Kaul, Nils Lager, Arvo Munoz Moran, Filip Tokarski, Gautam Vyas and Yidan Xu for reporting errors.

@@

This course will sample various aspects of modern mechanism design.
I'll begin by teaching a classical topic from a modern perspective.
The rest of the course will cover topics on the current research frontier, with a slant toward models in which monetary transfers are unavailable.
Along the way, we'll encounter a number of perspectives, tools, tricks and insights; these are just as important as the details of the models and papers themselves.

@@

% \emph{Topics:}
% the revelation principle;
% the envelope theorem \parencite{MilgromSegal2002,Sinander2022};
% Spence--Mirrlees characterisation of IC;
% the optimality of posting a price \parencite{Myerson1981};
% selling several goods \parencite[focus on examples from][]{HartReny2015};
% incentives via side bets \parencite{CremerMclean1985,CremerMclean1988,McafeeReny1992}.

@@

% \emph{Topics:}
% Border's theorem \parencite{Border1991};
% equivalence of dominant-strategy and Bayes--Nash IC in auctions \parencite{ManelliVincent2010};
% allocation with costly verification \parencite{BenporathDekelLipman2014};
% allocation with evidence acquisition (work in progress by the last authors);
% allocation with extra information \parencite{BlochDuttaDziubinski2021}.

@@

% \emph{Topics:}
% approximate optimality of (discounted) quotas \parencite{JacksonSonnenschein2007,Frankel2016jet};
% optimal mechanisms with commitment \parencite{GuoHorner2020};
% optimal mechanisms without commitment \parencite{LipnowskiRamos2020}.

@@

% \emph{Potential topics:}
% the original paper \parencite{ArmstrongVickers2010};
% random mechanisms \parencite{GuoShmaya2022};
% dynamic models \parencite{BirdFrug2019,sfb}.

>>>>

% % watermark on every page (for version control)
% \usepackage[anchor=ll,pos={0.1cm,0.5cm},fontsize=0.2cm,angle=0,alignment=l]{draftwatermark}
% \SetWatermarkText{\normalfont\hspace{0.37em}version:\\\normalfont {\datestyle\today}\\\normalfont\hspace{0.37em}at {\currenttime}}

@@

\date{\small This version: 6 November 2023}

@@

These are the notes for a second-year graduate course that I taught at Oxford in the autumns of 2021, 2022 and 2023.
Thanks to Gregorio Curello, Deniz Kattwinkel, Elliot Lipnowski, Qingmin Liu, Alex Teytelboym and to my students for comments, suggestions and insights,
and to Catharina Behrens, Josh le Cornu, Tanxin Gao, Brooklyn Han, Simon Handreke, Sanjari Kalantri, Marie Kaul, Nils Lager, Arvo Munoz Moran, Filip Tokarski, Gautam Vyas and Yidan Xu for reporting errors.

@@

This course will sample various aspects of modern mechanism design.
I'll begin by teaching a classical topic from a modern perspective.
The rest of the course will cover topics on (or close to) the current research frontier.
Along the way, we'll encounter a number of perspectives, tools, tricks and insights; these are just as important as the details of the models and papers themselves.

@@

@@

@@

@@
